Reflections on reflection for \\ intuitionistic set theories

### 2019-05-15 paper-reflection.tex
RRS_2 passes from the metatheory to sheaf models (WIP)

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\renewcommand{\SS}{\mathbb{S}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Mod}{Mod}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\length}{length}
\DeclareMathOperator{\List}{List}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}
\newcommand{\?}{\,{:}\,}
\newcommand{\realizes}{\Vdash}
\newcommand{\notnot}{\emph{not~not}\xspace}

@@

>>>>

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\renewcommand{\SS}{\mathbb{S}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Mod}{Mod}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\length}{length}
\DeclareMathOperator{\List}{List}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}
\newcommand{\?}{\,{:}\,}
\newcommand{\realizes}{\Vdash}
\newcommand{\notnot}{\emph{not~not}\xspace}
\newcommand{\speak}[1]{\ulcorner\text{\textnormal{#1}}\urcorner}

@@

Fourman and independently Hayashi have shown how to interpret~$\IZF$ in any
Grothendieck topos~\cite{fourman:izf,hayashi:izf}. The following proposition
shows that the axiom scheme~$\RRS_2$ passes from the metatheory to any such
model:

\begin{prop}Over~$\IZF + \RRS_2$, $\RRS_2$ holds in any Grothendieck topos.
\end{prop}

\begin{proof}We employ Streicher's version of the interpretation
of~$\IZF$~\cite{streicher:forcizf}, and follow him also in the notation.

Let~$\CC$ be a Grothendieck site, assumed without loss of generality to possess
a terminal object~$1$ and pullbacks. Let~$V$ be the universe sheaf over~$\CC$. Let
formulas~$\chi$ and~$\varrho$ be given, with parameters from~$V(1)$, defining
classes~$X$ and~$R$ in~$\Sh(\CC)$. Let an element~$x_0 \in V(1)$ be given and assume
\[ 1 \models \speak{$R \subseteq X \times X \times X$} \qquad\text{and}\qquad
  1 \models \speak{$R : X \times X \rightrightarrows X$}, \]
where the corner quotes indicate that translation to formal language is left to
the reader.

For an object~$I \in \CC$, let~$V_I$ be the (external) class of pairs~$(J
\xrightarrow{u} I, x \in V(J))$. Define the (external) classes
\begin{align*}
  X' &\defeq \{ (I,F) \,|\, I \in \CC, F \in P(V_I), \mathrm{fst}[F] \in
  \mathrm{Cov}(I), \forall (J \xrightarrow{u} I, x \in V(J)) \in F\_ J \models x \in X \}
\end{align*}
XXX
\end{proof}
